Coupling finite and boundary element methods to solve the Poisson-Boltzmann equation for electrostatics in molecular solvation

### 2023-04-25 main.tex
added graphical abstract

\begin{figure}[h]
\centering
\colorbox{background-color}{
\fbox{
\begin{minipage}{1.0\textwidth}
\includegraphics[width=50mm,height=50mm]{adaptive_mesh_fig.pdf} %Pick only one of the two styles by uncommenting the corresponding \includegraphics
%\includegraphics[width=110mm,height=20mm]{cc.eps}
\\
(75 words.) Images for the graphical Table of Contents should capture the essence of a paper, displaying a figure, plot, or scheme that is central to the theme of the manuscript. The text of the graphical Table of Contents is meant for the non-specialist and should ideally contain no obscure jargon or mathematical symbols / equations, but should attempt to convey the gist of the paper in everyday terms, while remaining consistent with accepted standards of scientific literature.
\end{minipage}
}}
\end{figure}

>>>>

\begin{figure}[h]
\centering
\colorbox{background-color}{
\fbox{
\begin{minipage}{1.0\textwidth}
\includegraphics[width=50mm,height=50mm]{graphical_abstract_fem-bem.png} %Pick only one of the two styles by uncommenting the corresponding \includegraphics
%\includegraphics[width=110mm,height=20mm]{cc.eps}
\\
    The boundary element method is, in many cases, the numerical algorithm of choice to solve the Poisson-Boltzmann equation for molecular electrostatics. However, this technique is limited to linear equations and piece-wise constant variations of the field parameters. Here, we overcome such limitations by coupling it with a finite element method, implemented with Bempp-cl and FEniCSx libraries through simple Python interfaces. This results in an accurate, flexible, and easy-to-use computational tool for model development. 
\end{minipage}
}}
\end{figure}
